%-------------------------
% IIT Guwahati Resume Template (CCD Format)
% Author: Ashutosh Yadav
%-------------------------
% NOTE: Place the IIT Guwahati logo as 'iitg_logo.png' in the same
%       directory as this .tex file. You can download it from:
%       https://www.iitg.ac.in or search "IIT Guwahati logo PNG"
%-------------------------

\documentclass[a4paper,11pt]{article}

%---------- PACKAGES ----------
\usepackage[empty]{fullpage}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[colorlinks=true, allcolors=black]{hyperref}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{multicol}

%---------- PAGE SETUP ----------
\geometry{
    left=0.5in,
    right=0.5in,
    top=0.4in,
    bottom=0.4in
}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%---------- SECTION FORMATTING ----------
\titleformat{\section}{
    \vspace{-8pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%---------- CUSTOM COMMANDS ----------
\newcommand{\resumeItem}[1]{
    \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{\small#1} & \small #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%---------- COLORS ----------
\definecolor{linkcolor}{HTML}{0066CC}
\hypersetup{
    colorlinks=true,
    linkcolor=linkcolor,
    urlcolor=linkcolor,
}

%====================  DOCUMENT START  ====================%
\begin{document}

%---------- HEADER (IITG CCD FORMAT) ----------
\begin{table}[ht]
    \begin{tabularx}{\textwidth}{@{}X r@{}}
        % ---------- CENTER: Student Details ----------
        \begin{tabular}[t]{@{}l@{}}
            {\large \textbf{\textit{Ashutosh Yadav}}} \\[2pt]
            \textbf{Roll No.: 23035010693} \\[1pt]
            \textbf{Online B.Sc. (Honours)} \\[1pt]
            \textbf{Data Science and Artificial Intelligence} \\[1pt]
            \textbf{Indian Institute of Technology, Guwahati}
        \end{tabular}
        &
        % ---------- RIGHT: Contact Info ----------
        \begin{tabular}[t]{r@{}}
            \faPhone\ +91 9628356778 \\[2pt]
            \faEnvelope\ \href{mailto:ashutosh.yadav@op.iitg.ac}{ashutosh.yadav@op.iitg.ac} \\[2pt]
            \faGlobe\ \href{https://ashutosh-yadav0001.github.io/my_portfolio/}{Portfolio} ~$|$~ \faLinkedin\ \href{https://www.linkedin.com/in/ashutosh0001/}{LinkedIn}
        \end{tabular}
        \\
    \end{tabularx}
\end{table}
\vspace{-16pt}
\noindent\rule{\textwidth}{1.2pt}
\vspace{-10pt}

%---------- CAREER OBJECTIVE ----------
\section{Career Objective}
\vspace{2pt}
\small{IT professional with 3+ years in endpoint management and cloud infrastructure, seeking to transition into software development and AI/ML engineering. Quick learner with strong Python, data science, and Azure foundations.}
\vspace{-2pt}

%---------- EDUCATION ----------
\section{Education}
\vspace{2pt}
\begin{center}
\small
\begin{tabularx}{0.97\textwidth}{|l|X|c|c|}
    \hline
    \textbf{Degree/Certificate} & \textbf{Institute/Board} & \textbf{CGPA/\%} & \textbf{Year} \\
    \hline
    B.Sc. (Hons) in Data Science \& AI & Indian Institute of Technology Guwahati & 8.5 (Current) & 2023 -- Present \\
    \hline
    Senior Secondary (XII) & CBSE Board & 87.2\% & 2021 \\
    \hline
    Secondary (X) & CBSE Board & 86.5\% & 2019 \\
    \hline
\end{tabularx}
\end{center}
\vspace{-6pt}

%---------- WORK EXPERIENCE ----------
\section{Work Experience}
\resumeSubHeadingListStart

    \resumeSubheading
        {MECM Administrator}{Oct 2023 -- Present}
        {HCL Technologies Ltd.}{Lucknow, India}
    \resumeItemListStart
        \resumeItem{Managed end-to-end SCCM patching lifecycle — SUG creation, update downloads, and production deployments — while creating daily client health check reports and remediation scripts for patch failures.}
        \resumeItem{Implemented Windows Autopilot for pre-provisioned deployment in production; captured custom Windows 10 images for product deployment cycles.}
        \resumeItem{Managed device compliance policies, app deployments, and configuration profiles via Microsoft Intune (MDM/MAM), enforcing security baselines and conditional access across Windows, iOS, and Android.}
        \resumeItem{Created and deployed app protection policies, device configuration profiles, and Windows update rings; troubleshot enrollment failures, sync issues, and policy conflicts.}
        \resumeItem{Administered Citrix Virtual Apps and Desktops environment — session management, infrastructure monitoring, and resolving connectivity and performance issues.}
        \resumeItem{Performed application onboarding and functional testing across DEV, UAT, and Production environments with Win32 packaging and DEV ring documentation.}
    \resumeItemListEnd

    \resumeSubheading
        {Training \& Internship Program}{Oct 2022 -- Oct 2023}
        {HCL Training \& Staffing Services Pvt. Ltd.}{Lucknow, India}
    \resumeItemListStart
        \resumeItem{Completed 1-year training and internship program conducted by HCL Training and Staffing Services.}
        \resumeItem{Gained hands-on experience in VMware, Azure, RDBMS, Active Directory, ITIL, and Networking.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%---------- KEY PROJECT ----------
\section{Key Project / Client Engagement}
\resumeSubHeadingListStart

    \resumeProjectHeading
        {Allianz -- Insurance and Asset Management Company}{Tools: SCCM \& Intune}
    \resumeItemListStart
        \resumeItem{Managed end-to-end application onboarding, functional testing, and DEV ring documentation across DEV, UAT, and Production environments.}
        \resumeItem{Handled SCCM patching lifecycle -- SUG creation, update downloads, and production deployments.}
        \resumeItem{Created, tested, and implemented conditional access policies; deployed remediation scripts for patch failures.}
        \resumeItem{Implemented Windows Autopilot for pre-provisioned deployments and captured custom Win10 images.}
        \resumeItem{Performed application packaging using Win32 Content Prep tool and supported SCCM-related technical issues.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%---------- ACADEMIC PROJECTS ----------
\section{Academic Projects}
\resumeSubHeadingListStart

    \resumeProjectHeading
        {Plant Disease Classification Using Deep Learning}{\href{https://github.com/Ashutosh-yadav0001/Pototo-disease}{GitHub}}
    \resumeItemListStart
        \resumeItem{Built an end-to-end web application for detecting diseases in Potato and Tomato leaves using Convolutional Neural Networks (CNN) with TensorFlow/Keras.}
        \resumeItem{Trained CNN models on publicly available datasets achieving high classification accuracy across multiple disease categories.}
        \resumeItem{Developed a RESTful API backend using Python and FastAPI for model inference and image processing.}
        \resumeItem{Created a responsive React.js frontend with image upload, real-time prediction display, and prediction history features.}
        \resumeItem{\textbf{Tech Stack:} Python, TensorFlow/Keras, FastAPI, React.js, NumPy, Pillow}
    \resumeItemListEnd

    \resumeProjectHeading
        {Sentinel-Sync: Edge-Cloud Collaborative Vision System}{}
    \resumeItemListStart
        \resumeItem{Designed a dual-tier AI architecture for industrial monitoring — edge-based YOLOv10-Nano for real-time object detection at 30+ FPS with selective cloud escalation via Gemini 1.5 Pro for visual reasoning.}
        \resumeItem{Implemented a ``Selective Trigger'' mechanism reducing cloud bandwidth costs by \textasciitilde90\% by filtering frames locally based on confidence thresholds and restricted-zone dwell time (>2s).}
        \resumeItem{Built an asynchronous MQTT/Protobuf communication pipeline achieving <500ms edge-to-cloud latency with FastAPI gateway and Redis caching for event logs.}
        \resumeItem{Developed a Streamlit dashboard for real-time alert visualization and AI reasoning logs with end-to-end detection-to-alert workflow.}
        \resumeItem{\textbf{Tech Stack:} Python, OpenCV, YOLOv10, TensorRT, MQTT, FastAPI, Redis, Gemini API, Docker, Streamlit}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%---------- TECHNICAL SKILLS ----------
\section{Technical Skills}
\vspace{2pt}
\small
\begin{tabularx}{0.97\textwidth}{@{}l X@{}}
    \textbf{Languages:} & Python, C, R, Java, SQL \\[3pt]
    \textbf{Data Science \& AI:} & Machine Learning, Data Analysis, Linear Algebra, Optimization, Econometrics \\[3pt]
    \textbf{Cloud \& Infra:} & Microsoft Azure, VMware, Active Directory, ITIL, Networking \\[3pt]
    \textbf{Tools \& Platforms:} & SCCM (MECM), Microsoft Intune, Windows Autopilot, Win32 Content Prep \\
\end{tabularx}
\vspace{-4pt}

%---------- RELEVANT COURSEWORK ----------
\section{Relevant Coursework}
\vspace{2pt}
\small
Data Structures \quad $\bullet$ \quad Algorithm Design \& Analysis \quad $\bullet$ \quad Computer System Tools \quad $\bullet$ \quad Data Science \quad $\bullet$ \quad Artificial Intelligence \quad $\bullet$ \quad Linear Algebra \quad $\bullet$ \quad Optimization \quad $\bullet$ \quad Econometrics
\vspace{-4pt}

%---------- CERTIFICATIONS ----------
\section{Licenses \& Certifications}
\vspace{2pt}
\begin{center}
\small
\begin{tabularx}{0.97\textwidth}{|X|c|c|c|}
    \hline
    \textbf{Certification} & \textbf{Earned On} & \textbf{Expires On} & \textbf{Link} \\
    \hline
    Microsoft Certified: Azure AI Engineer Associate (AI-102) & Feb 2026 & Feb 2028 & \href{https://learn.microsoft.com/api/credentials/share/en-us/AshutoshYadav-1786/B743EFD4D5570096?sharingId=20428F42E987074D}{\faExternalLink*} \\
    \hline
    Microsoft 365 Certified: Endpoint Administrator Associate & Jun 2024 & Jun 2026 & \href{https://learn.microsoft.com/api/credentials/share/en-us/AshutoshYadav-1786/B68119B3500414AA?sharingId=20428F42E987074D}{\faExternalLink*} \\
    \hline
    Microsoft Certified: Azure AI Fundamentals & May 2024 & N/A & \href{https://learn.microsoft.com/api/credentials/share/en-us/AshutoshYadav-1786/DF9E3A6A6FDA9800?sharingId=20428F42E987074D}{\faExternalLink*} \\
    \hline
\end{tabularx}
\end{center}
\vspace{-4pt}

%---------- POSITIONS OF RESPONSIBILITY ----------
\section{Positions of Responsibility}
\resumeSubHeadingListStart
    \resumeProjectHeading
        {Coordinator, Finance and Investment Club}{IIT Guwahati, 2026}
    \resumeItemListStart
        \resumeItem{Organizing workshops, speaker sessions, and events on topics related to personal finance, stock markets, and investment strategies.}
        \resumeItem{Collaborating with club members to promote financial literacy and awareness among the student community.}
        \resumeItem{Managing club communications, social media outreach, and coordination with other campus organizations.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}
